% sections/coverletter.tex - TAILORED FOR EMBEDDED DEVELOPER

\newpage

\import{sections/}{header}
\vspace{0.5cm}

\today

\vspace{0.6cm}

Dear Hiring Manager at [Company Name],

\vspace{0.4cm}

I am writing to express my strong interest in the Embedded Developer position. My background as a Computer Engineering student is uniquely complemented by a proven ability to design, build, and debug hardware systems from the ground up, and I am eager to apply this practical experience to your engineering team.

\vspace{0.2cm}
A successful embedded developer needs to bridge the gap between hardware and software. Here is how my experience aligns with that requirement:
\begin{itemize}[leftmargin=*, itemsep=0.5em]
  \item \textbf{Hardware Design and Prototyping}
    At a personal level, I have taken multiple projects from concept to market, including an N64 cartridge reader for which I designed and laid out a custom PCB in KiCad, assembled the boards with SMD hand-soldering, and modeled the enclosures.
    
  \item \textbf{Bare-Metal Firmware Development}
    I have extensive experience writing low-level C/C++ and Assembly firmware for microcontrollers like the RP2040 and ATmega/AVR. This includes implementing communication protocols like I2C and SPI from scratch and directly manipulating hardware registers to control peripherals.

  \item \textbf{Full Systems Integration}
    For my N64 reader project, I integrated all components into a functional commercial product, implementing a TinyUSB-based mass storage interface for seamless PC connectivity.

  \item \textbf{Diagnostics and Troubleshooting}
    I am proficient in using oscilloscopes, logic analyzers, and multimeters to debug embedded systems at the component level. My experience includes performing root-cause analysis on complex electromechanical systems to identify and resolve failures.
\end{itemize}

\vspace{0.2cm}
I am finishing my computer engineering degree on a part-time schedule, which allows me to maintain a strong focus on professional work. I have a genuine passion for building efficient, low-level solutions and making hardware come to life with software. I look forward to the chance to contribute to your projects and help develop robust and innovative products.

\vspace{0.4cm}
Thank you for your time and consideration. I would welcome the opportunity to discuss how my hands-on engineering skills can benefit [Company Name].

\vspace{0.6cm}
Sincerely,

\vspace{1cm}
Jayson Gazeley

\newpage